---
output: github_document
author: Lika Mikhelashvili, Adriana Beltran Andrade, Vibha Gogu
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# CodeGovern

### Purpose
Code Govern is a package used to scrape and imports and downloads datasets and metadata from the website Data.gov. This website is the federal government's open data site, and has over 298,424 datasets available to download in various export types (i.e. .csv, .xml, .json). Using CodeGovern functions, the data can be easily downloaded onto your computer, or for .csv files, return the data directly in RStudio.

## Target audience
This package is intended for users who want to work with open government data without having to repetitively download data and work with the Data.gov interface. 

##Installation 

### Dependencies/Setup
Need to load the following libraries:

```{r}
library(rvest)
library(stringr)
library("htmltools")
library("xml2")
library(tidyverse)
library(readr)
#install.packages("rjson")
library(rjson)
```

### Arguments

`name` is the name of the dataset you want to download. The name should be a string and should be worded exactly as it appears on the data.gov website. Example, "Lottery Powerball Winning Numbers Beginning 2010"

`type`: type of the data set. Must be a string. For example, "csv", "json", "xml", etc. 


### Result
The function returns a downloaded data file that the user can assign to an object and import into the RStudio environment. 


## Code

## Examples

```{r test examples}
name <- "Electric Vehicle Population Data"
# assignment happens like this:
my_data <- get_gov_file(name, "json")
name2 <- "Lottery Powerball Winning Numbers Beginning 2010"
# assignment happens like this:
my_data2 <- get_gov_file(name2, "xml")
```

## Testing

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/CodeGovern)](https://CRAN.R-project.org/package=CodeGovern)
<!-- badges: end -->

The goal of CodeGovern is to scrape and import datasets and metadata from government data websites like data.gov. 

## Installation

You can install the development version of CodeGovern like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
#library(CodeGovern)
## basic example code
```

