---
title: "CodeGovern"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CodeGovern}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CodeGovern)
```


## Dependencies/Setup
Need to load the following libraries:

```{r}
library(rvest)
library(stringr)
library("htmltools")
library("xml2")
library(tidyverse)
library(readr)
library(rjson)
```


### `get_gov_file`

#### Arguments

`name` is the name of the dataset you want to download. The name should be a string and should be worded exactly as it appears on the data.gov website. Example, "Lottery Powerball Winning Numbers Beginning 2010"

`type`: type of the data set. Must be a string. For example, "csv", "json", "xml", etc. 

`import`: Boolean that decides if file should be imported locally. By default it is TRUE and will import locally. Used mostly for internal processes. 


#### Result
The function returns a downloaded data file that the user can assign to an object and import into the RStudio environment. The function currently supports only three file types: CSV, JSON, and XML.

- CSV: the function will download the file locally and return a data frame.

- JSON: the function will download the file locally and return the raw JSON file.

- XML: the function will download the file locally.

If the user enters any other file types, the function will put an error message and redirect the user to the website of the data.


#### Examples

```{r eval = FALSE}
library(CodeGovern)
my_data1 <- get_gov_file("Electric Vehicle Population Data", "json")
my_data2 <-get_gov_file("Lottery Powerball Winning Numbers Beginning 2010", "csv")
```

### `federal_alert`

#### Arguements 
`name` is the name of the dataset you want to download. The name should be a string and should be worded exactly as it appears on the data.gov website. Example, "Lottery Powerball Winning Numbers Beginning 2010"

#### Result

The result is a string with either one of two messages: "This a Federal dataset covered by Data.gov's Terms of Use" or "Alert: This is a Non-Federal dataset covered by different Terms of Use than Data.gov". 

#### Examples
```{r eval = FALSE}
library(CodeGovern)
federal_alert("Electric Vehicle Population Data")
federal_alert("FDIC Failed Bank List")
```

### `explore_datasets`

#### Context
explore_datasets function is meant to be used with get_gov_file or get_many_gov_files to allow users to have a larger set of datasets they could call upon and use quickly. Because of that we have to limit our dataset search as those functions can only aid in downloading csv and JSON. Hopefully in the future we will be able to expand. The function also returns names given their popularity ranking on the website the moment you run the function, therefore you may not always get the same datasets even when putting the same parameters. 

#### Arguements 
`entries` Integer number of dataset names to collect. It needs to be larger than 1.

`format` Default is both JSON and CSV. Could select only one by "csv" or "json". Also included "all", which returns dataset of any format although it wont be compatible with get_gov_file. 

`OrgType` Only the inputs named on ?explore_datasets are valid. If indifferent to a certain organization type, just disregard parameter. 

#### Result

The result is a vector of length `entries` with the names of the datasets given the arguments chosen on the call.

#### Examples
```{r eval = FALSE}
library(CodeGovern)
# 2 Parameters, 2 pages
titles1 <- explore_datasets(25, format = "csv", OrgType = "Federal Government")

# no parameters, 1 page scraped
titles2 <- explore_datasets(10)

# no parameters,2 pages scraped
titles3 <- explore_datasets(30)

# 1 parameter, 1 page scraped
titles4 <- explore_datasets(10, format = "json")

# 1 parameter, 2 pages scraped
titles4 <- explore_datasets(30, OrgType = "University")

# two pages scraped of all formats
titles5 <- explore_datasets(30, format = "all")
```
