---
title: "CodeGovern"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{CodeGovern}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(CodeGovern)
```


## Dependencies/Setup
Need to load the following libraries:

```{r}
library(rvest)
library(stringr)
library("htmltools")
library("xml2")
library(tidyverse)
library(readr)
library(rjson)
```


### `get_gov_file`

#### Arguments

`name` is the name of the dataset you want to download. The name should be a string and should be worded exactly as it appears on the data.gov website. Example, "Lottery Powerball Winning Numbers Beginning 2010"

`type`: type of the data set. Must be a string. For example, "csv", "json", "xml", etc. 

`import`: Boolean that decides if file should be imported locally. By default it is TRUE and will import locally. Used mostly for internal processes. 


#### Result
The function returns a downloaded data file that the user can assign to an object and import into the RStudio environment. The function currently supports only three file types: CSV, JSON, and XML.

- CSV: the function will download the file locally and return a data frame.

- JSON: the function will download the file locally and return the raw JSON file.

- XML: the function will download the file locally.

If the user enters any other file types, the function will put an error message and redirect the user to the website of the data.


#### Examples

```{r eval = FALSE}
library(CodeGovern)
my_data1 <- get_gov_file("Electric Vehicle Population Data", "json")
my_data2 <-get_gov_file("Lottery Powerball Winning Numbers Beginning 2010", "csv")
```
